---
title: "Accountable Care Organizations"
output: 
  flexdashboard::flex_dashboard:
    theme: paper
runtime: shiny
---

```{r global, include=FALSE}
# load data in 'global' chunk so it can be shared by all users of the dashboard

library(tidyverse)
library(ggplot2)
library(flexdashboard)
library(usmap)

aco <- readRDS("clean_data/aco.RDS")
county <- readRDS("clean_data/county.RDS")

acos <- readRDS("clean_data/acos_regression.RDS")
patient <- readRDS("clean_data/patient_regression.RDS")
provider <- readRDS("clean_data/provider_regression.RDS")

```

Intro  {data-orientation=rows}
===================================== 
    
Value Box Rows
------------------------------------------------

### Total Number of Participating ACOs in 2018

```{r value_totalaco}
num_acos <- length(unique(aco$ACO_ID))
valueBox(num_acos, icon = "fa-hashtag")
```

### Number of New ACOs in 2018

```{r value_newaco}
num_new <- aco %>%
  filter(Initial_Start_Year == 2018) %>%
  nrow()

valueBox(num_new, icon = "fa-user-plus")
```

### Total Number of Participating Providers in 2018

```{r value_numproviders}
num_providers <- sum(aco$N_total_providers)
valueBox(prettyNum(num_providers, big.mark = ","), 
         icon = "fa-user-md")
```

### Total Number of Medicare Beneficiaries in 2018

```{r value_numbeneficiaries}
num_beneficiaries <- sum(aco$N_AB)
valueBox(prettyNum(num_beneficiaries, big.mark = ","), 
         icon = "fa-user-friends")
```




Description Row {.tabset .tabset-fade}
------------------------------------------------

### What are Accountable Care Organizations?

#### Origins

In 2008, Dr. Elliot Fisher introduced the concept of an "Accountable Care Organization" during a meeting with the Medicare Payment Advisory Committee ([MedPAC](http://www.medpac.gov/)) in reference to a new **payment arrangement** where all providers share accountability for the continuum a patient's care. 

An Accountable Care Organization is a groups of doctors, hospitals, and other health care providers who agree to be paid under a reimbursement system that aims to incentivize **high-quality coordinated care** for Medicare Patients. 

#### Video 

Kaiser Health News has a 3-minute informative introduction to ACOs: 

<p align="center"><iframe src='https://players.brightcove.net/1875348214/Sy7mrdF0_default/index.html?videoId=4441613712001&cms:wordpress:5.4:1.6.1:iframe' allowfullscreen frameborder=0; width=600px; height = 500px></iframe></p>




### Why ACOs? {data-commentary-width=100}

#### The Problem

There are two main problems facing the U.S. health care system. 

1. **Cost**: The U.S. spend *significantly* more on healthcare than all other countries

2. **Quality**: but under-performs on multiple indicators of health, including life expectancy, chronic disease burden, and avoidable deaths.

This problem is in part created by the incentives built into the way providers are paid. Medicare traditionally paid providers and hospitals through a **Fee For Service** (FFS) payment system. This creates an incentive to prioritize the *quantity* of services, without creating an incentive to promote higher **quality** of services. As a result, Medicare will pay for duplicate or unnecessary procedures, providers may recommend higher cost procedures over higher value services, and patients must assume responsiblity for coordinating their own care.

#### The Solution (?)

The ACO system tries to change the payment incentives to decrease spending for duplicate or low-value services. 

In this system, Medicare determines a **benchmark** or target amount of spending for an ACO.

* If ACOs spend less than the benchmark, they can split the savings with Medicare, and keep part of the savings.
* If ACOs spend more than the benchmark, they must pay the difference back to Medicare.

In order to prevent providers from skimping on care, they must also report on quality measures to remain eligible. 


### How do they work?


#### ACOs are responsible for:

- declaring which financial Track they would like to pursue.
  - ACOs in **Track 1** participate in one-sided risk (shared savings only)
  - ACOs in **Tracks 1+, 2, and 3** participate in two-sided risk (shared savings and shared losses).
- Providers see patients and send **claims** and bill CMS as they usually would Medicare beneficiaries
- Providing data on **quality measurements** to ensure they are eligible to share in any earned savings and avoid shared losses at the maximum level

#### CMS is reponsible for:

- assigning **beneficiaries** to the ACO by attributing beneficiaries to the providers from whom they receive the majority of their care.
- determine a **benchmark** based on prior expenditures, which sets a target for ACOs to limit their spending
- determining the **Minimum Loss Ratio** (MLR) / **Minimum Savings Ratio** (MSR) depending on the declared financial Track.
- processing **claims** data to determine total expenditures
- reconciling the difference between expenditures and the benchmark to determine whether or not savings or losses were incurred.

> For more information, you can read about the full process from CMS's [MSSP Methodology](https://www.cms.gov/Medicare/Medicare-Fee-for-Service-Payment/sharedsavingsprogram/Downloads/Shared-Savings-Losses-Assignment-Spec-V7.pdf)

### This Project

This project aims to see which variables can help us understand whether or not an ACO will generate Savings, Losses, or No Savings / Losses.

We can look at factors related to the ACO, the Patients assigned to the ACO, and the Provider mix in the ACO.

* ACO Factors
  - Starting Year
  - Ratio of Beneficiaries to Providers
  - Current Track type
  - Quality Score

* Patient Factors
  - Ages (% in age categories 0-64, 65-74, 75-84, 85+)
  - Gender (% Male or Female)
  
* Provider Factors
  - % Primary Care Providers
  - % Specialists
  - Number of Total Providers


Results 
=====================================     

Inputs {.sidebar}
-------------------------------------

Use the filters to see the results of how ACOs fared in 2018.

```{r}
checkboxGroupInput(inputId = "agree",
            label = "Agreement Type",
            choices = unique(aco$Agree_Type),
            # multiple = TRUE,
            selected = unique(aco$Agree_Type))

selectInput(inputId = "initial",
            label = "Initial Starting Year",
            choices = unique(aco$Initial_Start_Year),
            multiple = TRUE,
            selected = unique(aco$Initial_Start_Year))

selectInput(inputId = "current",
            label = "Current Track",
            choices = unique(aco$current),
            multiple = TRUE,
            selected = unique(aco$current))

sliderInput(inputId = "quality",
            label = "Quality Score",
            min = min(aco$QualScore),
            max = max(aco$QualScore),
            value = c(min(aco$QualScore), max(aco$QualScore)))

actionButton(inputId = "update",
             label = "Update")
```


Column
-------------------------------------

### RESULTS

There are 3 variables we can examine to look at performance results of ACOs in 2018.

1. Categories of Savings / Losses
2. Amounts ($) of Savings / Losses
3. Rates of Savings / Losses


**Observations**

* ACOs that stay in the game tend to see greater savings. However, the number of ACOs that still participate in 2018 decreases as you go back to earlier years.
* Those who are in their renewal agreement (3 year contract) will generally see more savings compared to those in their initial agreement.
* ACOs in Track 1 do not perform as well as those in other Tracks. This may be confounded by the fact that new ACOs tend to start in Track 1.
* Higher Quality Scores show better results for ACOs in Tracks 1+, 2, and 3.

### Number of ACOs Selected

```{r}
renderValueBox ({
  
  input$update
  
  isolate({ 
    num <- aco %>%
    filter(
        Agree_Type %in% input$agree,
        current %in% input$current,
        Initial_Start_Year %in% input$initial,
        QualScore >= input$quality[1] & QualScore <= input$quality[2]
      ) %>%
    nrow()
    
    valueBox(num, icon = "fa-hashtag")
    
    })
  
})
```


### 1. Categories of Savings / Losses


```{r}
renderPlot({
  
  input$update
  
  isolate({
    aco %>%
      filter(
        Agree_Type %in% input$agree,
        current %in% input$current,
        Initial_Start_Year %in% input$initial,
        QualScore >= input$quality[1] & QualScore <= input$quality[2]
      ) %>%
      count(GenSaveLoss_categorical) %>%
      ggplot(aes(x = GenSaveLoss_categorical, y = n)) +
      geom_col(aes(fill = GenSaveLoss_categorical)) +
      geom_text(aes(y = n + 10, label = n)) +
      theme_minimal() +
      theme(
        panel.grid = element_blank(),
        legend.position = "none",
        axis.title = element_blank(),
        axis.text.y = element_blank()
      )
    
  })
})
```


Column
-------------------------------------
    
    
### 2. Amounts ($) of Savings / Losses

```{r}
renderPlot({
  
  input$update
  
  isolate({
    aco %>%
      filter(
        Agree_Type %in% input$agree,
        current %in% input$current,
        Initial_Start_Year %in% input$initial,
        QualScore >= input$quality[1] & QualScore <= input$quality[2]
      ) %>%
      ggplot(aes(x = BnchmkMinExp)) +
      geom_density(aes(fill = GenSaveLoss_categorical), alpha = 0.4) +
      geom_density(linetype = "dotted") +
      theme_minimal() +
      labs(x = "$ Amount",
           y = "Density",
           fill = "Category") +
      theme(
        panel.grid = element_blank(),
        axis.text.y = element_blank(),
        legend.position = "bottom"
      )
    
  })
})
```

> **Benchmark** (total amount allotted for all beneficiaries)  minus the **Expenditure** (total amount submitted in claims)

### 3. Rates of Savings / Losses

```{r}
renderPlot({
  
  input$update
  
  isolate({
    aco %>%
      filter(
        Agree_Type %in% input$agree,
        current %in% input$current,
        Initial_Start_Year %in% input$initial,
        QualScore >= input$quality[1] & QualScore <= input$quality[2]
      ) %>%
      ggplot(aes(x = Sav_rate)) +
      geom_density(aes(fill = GenSaveLoss_categorical), alpha = 0.4) +
      geom_density(linetype = "dotted") +
      theme_minimal() +
      labs(x = "Rates",
           y = "Density",
           fill = "Category") +
      theme(
        panel.grid = element_blank(),
        axis.text.y = element_blank(),
        legend.position = "bottom"
      )
    
  })
})
```

> **Savings Rate** = Benchmark - Expenditure / Benchmark. This metric shows the relative size of the gains or losses, normalized by the benchmark amount. 

Models
=====================================   


Regression {.sidebar}
-------------------------------------

Here we examine the effects of Patient, Provider, and ACO factors (explanatory variables) on the **Savings Rate** (outcome variable) using a multi-variate linear regression. The results of the 100 simulations of the regression are plotted. Each row represents the estimate with error bars produced by a single simulation.

*Dropdowns only work on corresponding panels*


```{r}
selectInput(inputId = "patient_term",
            label = "Patient Factors",
            choices = patient$term,
            selected = unique(patient$term)[1])

selectInput(inputId = "provider_term",
            label = "Provider Factors",
            choices = provider$term,
            selected = unique(provider$term)[1])

selectInput(inputId = "aco_term",
            label = "ACO Factors",
            choices = acos$term,
            selected = "Intercept") 
```



Regression {.tabset}
-------------------------------------

### Patient

```{r}
renderPlot({
  
  mean <- patient %>% filter(term == input$patient_term) %>%
    pull(estimate) %>%
    mean()
  
  patient %>%
    filter(term == input$patient_term) %>%
    ggplot(aes(x = reorder(replicate,-estimate))) +
    geom_point(aes(y = estimate, color = estimate > 0)) +
    geom_errorbar(aes(ymin = conf.low, ymax = conf.high)) +
    geom_hline(yintercept = mean) +
    coord_flip() +
    theme_minimal() +
    theme(
      axis.text.y = element_blank(),
      axis.ticks = element_blank(),
      panel.grid.major.y = element_blank()
    ) +
  labs(
    x = "Savings Rate Estimate",
    y = "Simulations",
    subtitle = "Results of 100 Simulations",
    title = paste("Mean of Estimates of ", input$patient_term, "is ", round(mean, 3))
  )
})
```


> **Intercept**: The average savings rate when all other variables are equal to 0. Defaults are: All beneficiaries are 0-64 and female.
  **% Beneficiaries Age 65-74** : The average change in Savings Rate with a 1% increase in the percentage of Beneficiaries between ages 65-74, holding all other variables constant.
  **% Beneficiaries Age 75-84** : The average change in Savings Rate with a 1% increase in the percentage of Beneficiaries between ages 75-84, holding all other variables constant.
  **% Beneficiaries Age 85+** : The average change in Savings Rate with a 1% increase in the percentage of Beneficiaries age 85 and older, holding all other variables constant.
  **% Beneficiaries Male** : The average change in Savings Rate with a 1% increase in the percentage of male beneficiares, holding all other variables constant.

### Providers

```{r}
renderPlot({
  
  # patient %>% head()
  
  mean <- provider %>% filter(term == input$provider_term) %>%
    pull(estimate) %>%
    mean()
  
  provider %>%
    filter(term == input$provider_term) %>%
    ggplot(aes(x = reorder(replicate,-estimate))) +
    geom_point(aes(y = estimate, color = estimate > 0)) +
    geom_errorbar(aes(ymin = conf.low, ymax = conf.high)) +
    geom_hline(yintercept = mean) +
    coord_flip() +
    theme_minimal() +
    theme(
      axis.text.y = element_blank(),
      axis.ticks = element_blank(),
      panel.grid.major.y = element_blank()
    ) +
  labs(
    x = "Savings Rate Estimate",
    y = "Simulations",
    subtitle = "Results of 100 Simulations of Linear Regression",
    title = paste("Mean of Estimates of ", input$provider_term, "is ", round(mean, 3))
  )
})
```

> **Intercept**: The average savings rate when all other variables are equal to 0. Defaults are: 0%     PCPs, 0% Specialists, 0 Providers. This value does not have a meaningful interpretation in this   context.
  **% PCP Providers** : The average change in Savings Rate with a 1% increase in the number of PCP Providers, holding all other variables constant.
  **% Specialist Providers**: The average change in Savings Rate with a 1% increase in the number of Specialist Providers, holding all other variables constant.
  **Number of Total Providers**: The average change in Savings Rate when the number of any type of providers increases by 100, holding all other variables constant.



### ACO

```{r}
renderPlot({
  
  # patient %>% head()
  
  mean <- acos %>% filter(term == input$aco_term) %>%
    pull(estimate) %>%
    mean()
  
  acos %>%
    filter(term == input$aco_term) %>%
    ggplot(aes(x = reorder(replicate,-estimate))) +
    geom_point(aes(y = estimate, color = estimate > 0)) +
    geom_errorbar(aes(ymin = conf.low, ymax = conf.high)) +
    geom_hline(yintercept = mean) +
    coord_flip() +
    theme_minimal() +
    theme(
      axis.text.y = element_blank(),
      axis.ticks = element_blank(),
      panel.grid.major.y = element_blank()
    ) +
  labs(
    x = "Savings Rate Estimate",
    y = "Simulations",
    subtitle = "Results of 100 Simulations",
    title = paste("Mean of Estimates of ", input$aco_term, "is ", round(mean, 3))
  )
})
```

> **Intercept**: The average savings rate when all other variables are equal to 0. Defaults are: Initial Starting Year in 2012, ratio of Assigned Beneficiaries to Providers is 0, ACO in Track 1, Quality Score is 0.
  **Initial Starting Year**: The average change in Savings Rate in the selected starting year compared to the 2012, holding all other variables constant.
  **Ratio of Assigned Beneficiaries to Providers**: The average change in Savings Rate when the ratio of increased by 1 unit, holding all other variables constant.
  **Track**: The average change in Savings Rate for ACOs in selected track compared to Track 1, holding all other variables constant.
  **Quality Score**: The average change in Savings Rate when the Quality Score increases by 1%, holding all other variables constant.






States {data-navmenu="Maps"}
=====================================   


Input {.sidebar}
-------------------------------------

```{r}
selectInput(inputId = "state",
            label = "State",
            choices = county$state_name)

selectInput(inputId = "beneficiary",
            label = "Beneficiary Type",
            choices = county$Beneficiary,
            selected = "End Stage Renal Disease")
```

Eligibility groups:

* **End Stage Renal Disease** patients with ESRD can receive Medicare coverage, regardless of age
* **Disabled** patients with qualifying disabilities can receive Medicare coverage may, regardless of age
* **Aged Non Dual** patients 65 and older and only enrolled in Medicare
* **Aged Dual** patients 65 and older and enrolled in both Medicaid and Medicare

```{r}
selectInput(inputId = "category",
            label = "Category",
            choices = county$Category,
            selected = "Per Capita Expenditures")
```


Output 
-------------------------------------

### State Maps

```{r}
renderPlot({
  d <- county %>%
    filter(Beneficiary == input$beneficiary,
           Category == input$category) 
  
  plot_usmap(data = d,
             regions = "counties",
             include = input$state,
             values = "Values",
             color = "white") +
    # scale_fill_continuous(low = "#DFF0EA", high = "#2A7886") +
    theme(legend.position = "bottom",
          legend.direction = "horizontal",
          legend.text = element_text(angle = 45, 
                                     hjust = 1, 
                                     vjust = 1)
          ) + 
    labs(
      title = paste(input$beneficiary, "Beneficiaries in ", input$state),
      subtitle = paste("by ", input$category),
      fill = paste(input$category)
    )

})
```

> Data is aggregated at a county level. This map is meant to show a distribution of patient characteristics in each state by county.

Summary {data-width=300}
-------------------------------------

### Beneficiary Summary

```{r}

renderPlot({
   county %>%
    group_by(Beneficiary, Category, state_name) %>%
    summarize(Values = sum(Values, na.rm = TRUE)) %>%
    filter(state_name == input$state,
           Category == input$category) %>%
    ggplot(aes(x = Beneficiary, y = Values)) +
    geom_col() +
    theme_minimal() +
    theme(
      panel.grid.major.y = element_blank(),
      panel.grid.minor.x = element_blank(),
      axis.title = element_blank()
    ) +
    labs(title = paste(input$category),
         subtitle = paste("in", input$state, sep = " ")) +
    coord_flip()
})
```

### Average Person Years by State

```{r}

py <- reactive({
  county %>%
    filter(state_name == input$state,
           Category == "Person Years") %>%
    summarize(Values = mean(Values, na.rm = TRUE)) %>%
    round(.)
})

renderValueBox({
  valueBox(py(), icon = "fa-stopwatch")
})
```


### Average Per Capita Expenditures by State

```{r}

pce <- reactive({
  county %>%
    filter(state_name == input$state,
           Category == "Per Capita Expenditures") %>%
    summarize(Values = mean(Values, na.rm = TRUE)) %>%
    round(.)
})

renderValueBox({

  valueBox(prettyNum(paste("$", pce()), 
    big.mark = ","), 
    icon = "fa-dollar-sign")
})

```

### Average HCC Risk Score by State


```{r}

risk <- reactive({
  county %>%
    filter(state_name == input$state,
           Category == "Average HCC Risk Score") %>%
    summarize(Values = mean(Values, na.rm = TRUE)) %>%
    round(., 2)
})

renderValueBox({
  valueBox(risk(), icon = "fa-exclamation")
})

```

Country {data-navmenu="Maps"}
=====================================   


Input {.sidebar}
-------------------------------------

There are 4 groups of beneficiaries that are eligible for Medicare coverage. 

```{r}
selectInput(inputId = "beneficiary_2",
            label = "Beneficiary Type",
            choices = county$Beneficiary)
```

Eligibility groups:

* **End Stage Renal Disease** patients with ESRD can receive Medicare coverage, regardless of age
* **Disabled** patients with qualifying disabilities can receive Medicare coverage may, regardless of age
* **Aged Non Dual** patients 65 and older and only enrolled in Medicare
* **Aged Dual** patients 65 and older and enrolled in both Medicaid and Medicare



Output {.tabset}
-------------------------------------

### Person Years

Person Years are a more precise way of measuring the amount of people in Medicare provides services to each year by counting people proportional to the time they are in the Medicare program. For example, someone who turns 65 in March would contribute 3/4ths of a person-year.

```{r map_personyear}

renderPlot({
  c <- county %>% 
    filter(Beneficiary == input$beneficiary_2,
           Category == "Person Years")
  
  plot_usmap(data = c,
             regions = "counties",
             values = "Values",
             color = "white",
             selected = "Aged Non-Dual") +
    scale_fill_continuous(low = "#DFF0EA", high = "#2A7886") +
    labs(fill = "Person Years") + 
    theme(legend.position = "right",
          legend.direction = "vertical")
  
})

```

> Data is aggregated at a county level. This map is meant to show a distribution of patient characteristics nationwide by county.


### Risk Adjustment 

Risk Adjustment Factors are calculated to modify patients for higher degrees of illness, based on patient demographics and Hierarchical Condition Categories (HCC). Risk adjustment scores are normalized around 1.0, and range from around 0.9 to 1.7. These are then multiplied to a dollar amount to set the expected expenditure and capitation for that individual. 

```{r map_riskadjust}

renderPlot({
  c <- county %>% 
    filter(Beneficiary == input$beneficiary_2,
           Category == "Average HCC Risk Score")
  
  plot_usmap(data = c,
             regions = "counties",
             values = "Values",
             color = "white",
             selected = "Aged Non-Dual") +
    scale_fill_continuous(low = "#DFF0EA", high = "#2A7886") +
    labs(fill = "Risk Adjustment Score") + 
    theme(legend.position = "right",
          legend.direction = "vertical")
  
})

```



### Per Capita Expenditures

Annualized, truncated, weighted mean total expenditures per beneficiary person year in the county.

```{r map_expenditure}

renderPlot({
  c <- county %>% 
    filter(Beneficiary == input$beneficiary_2,
           Category == "Per Capita Expenditures")
  
  plot_usmap(data = c,
             regions = "counties",
             values = "Values",
             color = "white",
             selected = "Aged Non-Dual") +
    scale_fill_continuous(low = "#DFF0EA", high = "#2A7886") +
    labs(fill = "Per Capita Expenditures ($)") +
    theme(legend.position = "right",
          legend.direction = "vertical")
  
})

```


Summary {data-width=300}
-------------------------------------


### Total Person Years by Beneficiary

```{r}
renderPlot({
  county %>%
    filter(Category == "Person Years") %>%
    group_by(Beneficiary) %>%
    summarise(Values = sum(Values, na.rm = TRUE)) %>%
    ggplot(aes(x = Beneficiary, y = Values)) +
    geom_col(aes(fill = Beneficiary), na.rm = TRUE) +
    theme_minimal() +
    theme(
      panel.grid = element_blank(),
      axis.title = element_blank(),
      legend.position = "none"
    ) +
    coord_flip()
})  
```


### Average HCC Risk Score by Beneficiary

```{r}
renderPlot({
  county %>%
    filter(Category == "Average HCC Risk Score") %>%
    group_by(Beneficiary) %>%
    summarize(Values = mean(Values, na.rm = TRUE)) %>%
    ggplot(aes(x = Beneficiary, y = Values)) +
    geom_col(aes(fill = Beneficiary)) +
    theme_minimal() +
    theme(
      panel.grid = element_blank(),
      axis.title = element_blank(),
      legend.position = "none"
    ) +
    coord_flip()
})
```


### Average Per Capita Expenditures by Beneficiary

```{r}
renderPlot({
  county %>%
    filter(Category == "Per Capita Expenditures") %>%
    group_by(Beneficiary) %>%
    summarize(Values = mean(Values, na.rm = TRUE)) %>%
    ggplot(aes(x = Beneficiary, y = Values)) +
    geom_col(aes(fill = Beneficiary)) +
    theme_minimal() +
    theme(
      panel.grid = element_blank(),
      axis.title = element_blank(),
      legend.position = "none"
    ) +
    coord_flip()
})
```


About 
===================================== 


Data Sources {data-width=750}
-------------------------------------

### Data Sources

#### ACO Data

2018 Shared Savings Program (SSP) 
Accountable Care Organizations (ACO)
Public Use File 

To address the increasing number of requests for SSP ACO data, the Centers for Medicare (CM) has created a standard analytical file that CMS can use to efficiently satisfy these requests. It is the intent of CM to publish the ACO-level public-use file (PUF) that contains ACO-specific metrics as well as summarized beneficiary and provider information for each performance year of the SSP program.

https://data.cms.gov/Special-Programs-Initiatives-Medicare-Shared-Savin/2018-Shared-Savings-Program-SSP-Accountable-Care-O/v47u-yq84

#### Beneficiaries by County Data 

Aggregate data consisting of per capita Parts A and B FFS expenditures, average CMS-HCC prospective risk scores and total person-years for assignable beneficiaries by Medicare enrollment type (End Stage Renal Disease (ESRD), disabled, aged/dual eligible, aged/non-dual eligible). It is the intent of CM to publish this PUF annually, in the summer following the conclusion of the calendar year to which it relates.

https://data.cms.gov/Special-Programs-Initiatives-Medicare-Shared-Savin/2018-County-level-FFS-Data-for-Shared-Savings-Prog/sju4-8k6c"


> Source code for this project is available on Github [here](https://github.com/karenmjiang/MSSP-ACO-2018).

About
-------------------------------------

### About Me

#### My name is Karen Jiang 

I am MPH Candidate in Health Policy at the [**Harvard T. H. Chan School of Public Health**](https://www.hsph.harvard.edu/). I am interested in using data visualization and communication as an advocacy tool to bring to light health disparities and help make better decisions about health policy.

### Contact Info

#### Connect with me via...

`r icon::fa("envelope")` Email:

* karenjiang@hsph.harvard.edu
* karenmjiang@gmail.com

`r icon::fa("linkedin-in")` LinkedIn:

* [linkedin.com/in/karenmjiang](https://www.linkedin.com/in/karenmjiang/)

`r icon::fa("github")` Github:

* [github.com/karenmjiang](https://github.com/karenmjiang)


