---
title: "Intro"
output: 
  flexdashboard::flex_dashboard:
    orientation: rows
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)

library(tidyverse)
library(ggplot2)
library(flexdashboard)

aco <- readRDS(file = "data/aco.RDS")
county <- readRDS(file = "data/county.RDS")
system <- read.csv(file = "data/healthsystemdata.csv")
```




Row 
------------------------------------------------

### Total Number of Participating ACOs in 2018

```{r}
num_acos <- length(unique(aco$ACO_ID))
valueBox(num_acos, icon = "fa-hashtag")
```

### Number of New ACOs

```{r}
num_new <- aco %>%
  filter(Initial_Start_Year == 2018) %>%
  nrow()

valueBox(num_new, icon = "fa-user-plus")
```

### Total Number of Participating Providers 

```{r}
num_providers <- sum(aco$N_total_providers)
valueBox(prettyNum(num_providers, big.mark = ","), 
         icon = "fa-user-md")
```

### Total Number of Medicare Beneficiaries 

```{r}
num_beneficiaries <- sum(aco$N_AB)
valueBox(prettyNum(num_beneficiaries, big.mark = ","), 
         icon = "fa-user-friends")
```


Row {.tabset .tabset-fade}
------------------------------------------------

### What are Accountable Care Organizations?

#### Origins

In 2008, Dr. Elliot Fisher introduced the concept of an "Accountable Care Organization" during a meeting with the Medicare Payment Advisory Committee ([MedPAC](http://www.medpac.gov/)) in reference to a new **payment arrangement** where all providers share accountability for the continuum a patient's care. 

An Accountable Care Organization is a groups of doctors, hospitals, and other health care providers who agree to be paid under a reimbursement system that aims to incentivize **high-quality coordinated care** for Medicare Patients. 


#### Video 

Kaiser Health News has a 3-minute informative introduction to ACOs: 

<p align="center"><iframe src='https://players.brightcove.net/1875348214/Sy7mrdF0_default/index.html?videoId=4441613712001&cms:wordpress:5.4:1.6.1:iframe' allowfullscreen frameborder=0; width=600px; height = 500px></iframe></p>




### Why ACOs? {data-commentary-width=100}



#### The Problem

There are two main problems facing the US health care system. 

1. **Cost**: We spend *significantly* more on healthcare than all other countries
2. **Quality**: And yet, we've seen a decline in life expectancy for the past 3 years

Medicare traditionally paid providers and hospitals through a **Fee For Service** (FFS) payment system. That is, payments are made to providers and hospitals for each service provided.

This creates an incentive to prioritize the *quantity* of services over the *quality* of services. As a result, we see duplicative services and poor coordination of care for patients, which ultimately lead to poor outcomes.

```{r, fig.align="center"}

us <- system %>%
  head(1)

system %>%
  ggplot(aes(x = GDP.per.capita, y = Health.spending.per.capita)) +
  geom_point() +
  geom_abline(aes(slope = 0.1, intercept = 0), alpha = 0.8, linetype = "dashed") + 
  geom_point(data = us, 
             aes(x = GDP.per.capita, y = Health.spending.per.capita), 
             color = "red") +
  geom_text(data = us, 
            aes(x = GDP.per.capita, y = Health.spending.per.capita, label = X2017),
            nudge_y = -500) +
  scale_x_continuous(breaks = c(20000,40000,60000,80000,100000),
                     labels = c("20k", "40k", "60k", "80k", "100k")) +
  scale_y_continuous(breaks = c(2000,4000,6000,8000,10000),
                     labels = c("2k", "4k", "6k", "8k", "10k")) +
  theme_classic() +
  theme(
    axis.ticks = element_blank(),
    axis.line = element_blank(),
    panel.grid.major = element_line(color = "gray", size = 0.2)
  ) +
  labs(
    x = "GDP Per Capita",
    y = "Health Spending per Capita",
    caption = "Source: Peterson KFF Health System Tracker 2017 "
  )
```


### How do they work?

The following is a very pared down version of how ACOs

#### ACOs are responsible for:

- declaring which financial Track they would like to pursue.
  - ACOs in **Track 1** participate in one-sided risk (shared savings only)
  - ACOs in **Tracks 1+, 2, and 3** participate in two-sided risk (shared savings and shared losses).
- Providers see patients and send **claims** and bill CMS as they usually would Medicare beneficiaries
- Providing data on **quality measurements** to ensure they are eligible to share in any earned savings and avoid shared losses at the maximum level


#### CMS is reponsible for:

- assigning **beneficiaries** to the ACO by attributing beneficiaries to the providers from whom they receive the majority of their care.
- determine a **benchmark** based on prior expenditures, which sets a target for ACOs to limit their spending
- determining the **Minimum Loss Ratio** (MLR) / **Minimum Savings Ratio** (MSR) depending on the declared financial Track.
- processing **claims** data to determine total expenditures
- reconciling the difference between expenditures and the benchmark to determine whether or not savings or losses were incurred.


> For more information, you can read about the full process from CMS's [MSSP Methodology](https://www.cms.gov/Medicare/Medicare-Fee-for-Service-Payment/sharedsavingsprogram/Downloads/Shared-Savings-Losses-Assignment-Spec-V7.pdf)
