---
title: "Models"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)

library(tidyverse)
library(ggplot2)
library(plotly)
library(broom)
library(gt)
library(tidymodels)
library(rpart.plot)

aco <- readRDS(file = "data/aco.RDS")
county <- readRDS(file = "data/county.RDS")
```


We would want to run a model that can help predict the **Savings Rate** and **Generated Savings / Losses Category**. 

## Hypothesis

I hypothesize that 3 factors can help predict the savings rate for an ACO. 

* ACO Factors
  - Starting Year
  - Ratio of Beneficiaries to Providers
  - Current Track type
  - Quality Score
  - Number of States
  
* Patient Factors
  - Ages (% in age categories 0-64, 65-74, 75-84, 85+)
  - Gender (% Male or Female)
  
* Provider Factors
  - % Primary Care Providers
  - % Specialists
  
  
```{r}
colnames(aco)
```

# Classification

```{r}
smp_size <- floor(0.75 * nrow(aco))

train_ind <- sample(nrow(aco), size = smp_size)

train <- aco[train_ind, ]
test <- aco[-train_ind, ]

```

  
## ACO Factors
  
```{r}

cart_mod <- decision_tree() %>%
  set_engine("rpart",
             model = TRUE) %>%
  set_mode("classification")


cart_fit <- fit(cart_mod,
                    as.factor(GenSaveLoss_categorical) ~ Initial_Start_Year + ratio_AB_to_providers + current + QualScore + num_states,
                    data = train)



forest_mod <- rand_forest(mtry = 7, trees = 100) %>%
  set_engine("randomForest") %>%
  set_mode("classification")

forest_fit <- fit(forest_mod,
                    as.factor(GenSaveLoss_categorical) ~ Initial_Start_Year + ratio_AB_to_providers + current + QualScore + num_states,
                    data = train)


predictions <- test %>%
  mutate(cart = predict(cart_fit, test) %>% 
           pull(.pred_class),
         forest = predict(forest_fit, test) %>%
           pull(.pred_class)
  )

aco_factor <- tibble(
  cart = mean(predictions$cart == predictions$GenSaveLoss_categorical),
  forest = mean(predictions$forest == predictions$GenSaveLoss_categorical)
) 

```

## Patient Factors  

```{r}
cart_mod <- decision_tree() %>%
  set_engine("rpart",
             model = TRUE) %>%
  set_mode("classification")


cart_fit <- fit(cart_mod,
                    as.factor(GenSaveLoss_categorical) ~ perc_Age_0_64 + perc_Age_65_74 + perc_Age_75_84 + perc_Age_85plus + perc_male,
                    data = train)



forest_mod <- rand_forest(mtry = 7, trees = 100) %>%
  set_engine("randomForest") %>%
  set_mode("classification")

forest_fit <- fit(forest_mod,
                     as.factor(GenSaveLoss_categorical) ~ perc_Age_0_64 + perc_Age_65_74 + perc_Age_75_84 + perc_Age_85plus + perc_male,
                    data = train)


predictions <- test %>%
  mutate(cart = predict(cart_fit, test) %>% 
           pull(.pred_class),
         forest = predict(forest_fit, test) %>%
           pull(.pred_class)
  )

patient_factor <- tibble(
  cart = mean(predictions$cart == predictions$GenSaveLoss_categorical),
  forest = mean(predictions$forest == predictions$GenSaveLoss_categorical)
)

```

## Provider Factors

```{r}
cart_mod <- decision_tree() %>%
  set_engine("rpart",
             model = TRUE) %>%
  set_mode("classification")


cart_fit <- fit(cart_mod,
                    as.factor(GenSaveLoss_categorical) ~ perc_PCP + perc_Spec + N_total_providers,
                    data = train)



forest_mod <- rand_forest(mtry = 7, trees = 100) %>%
  set_engine("randomForest") %>%
  set_mode("classification")

forest_fit <- fit(forest_mod,
                     as.factor(GenSaveLoss_categorical) ~ perc_PCP + perc_Spec + N_total_providers,
                    data = train)


predictions <- test %>%
  mutate(cart = predict(cart_fit, test) %>% 
           pull(.pred_class),
         forest = predict(forest_fit, test) %>%
           pull(.pred_class)
  )

provider_factor <- tibble(
  cart = mean(predictions$cart == predictions$GenSaveLoss_categorical),
  forest = mean(predictions$forest == predictions$GenSaveLoss_categorical)
)
```


## Kitchen Sink

```{r}

cart_mod <- decision_tree() %>%
  set_engine("rpart",
             model = TRUE) %>%
  set_mode("classification")


cart_fit <- fit(cart_mod,
                    as.factor(GenSaveLoss_categorical) ~ Initial_Start_Year + ratio_AB_to_providers + current + QualScore + num_states + perc_Age_0_64 + perc_Age_65_74 + perc_Age_75_84 + perc_Age_85plus + perc_male + perc_PCP + perc_Spec + N_total_providers,
                    data = train)



forest_mod <- rand_forest(mtry = 7, trees = 100) %>%
  set_engine("randomForest") %>%
  set_mode("classification")

forest_fit <- fit(forest_mod,
                    as.factor(GenSaveLoss_categorical) ~ Initial_Start_Year + ratio_AB_to_providers + current + QualScore + num_states + perc_Age_0_64 + perc_Age_65_74 + perc_Age_75_84 + perc_Age_85plus + perc_male + perc_PCP + perc_Spec + N_total_providers,
                    data = train)


predictions <- test %>%
  mutate(cart = predict(cart_fit, test) %>% 
           pull(.pred_class),
         forest = predict(forest_fit, test) %>%
           pull(.pred_class)
  )

all_vars <- tibble(
  cart = mean(predictions$cart == predictions$GenSaveLoss_categorical),
  forest = mean(predictions$forest == predictions$GenSaveLoss_categorical)
)

```


```{r}
results <- bind_rows(aco_factor, patient_factor, provider_factor, all_vars, .id = "ID") %>%
  mutate(factors = c("ACO Factors", "Patient Factors", "Provider Factors", "All Factors")) %>%
  pivot_longer(cols = c(cart, forest), names_to = "method", values_to = "prediction")

getmode <- function(v) {
   uniqv <- unique(v)
   uniqv[which.max(tabulate(match(v, uniqv)))]
}
getmode(train$GenSaveLoss_categorical)

mode <- mean(getmode(train$GenSaveLoss_categorical) == predictions$GenSaveLoss_categorical)

results %>%
 ggplot(aes(x = reorder(factors, as.numeric(ID)), y = prediction)) + geom_col(aes(fill = method), position = "dodge") + 
  geom_hline(yintercept = mode)
  theme_minimal()
```


```{r}
aco %>%
  filter(current != "Track 1") %>%
  ggplot(aes(x = Sav_rate, y=GenSaveLoss)) + geom_point()
```




# Regression





## ACO metrics



### Linear Regression Table

Relationship between starting year and generated savings

```{r}
aco %>%
  mutate(
    Initial_Start_Year = as.numeric(Initial_Start_Year)
    ) %>%
  lm(GenSaveLoss ~ Initial_Start_Year, .) %>%
  tidy(conf.int = TRUE) %>%
  select(term, estimate, conf.low, conf.high) %>%
  gt() %>%
  tab_header(
    title = "Linear Regression of Initial Start Year on Generated Savings / Losses"
  ) %>%
  cols_label(
    term = "Variable",
    estimate = "Estimate",
    conf.low = "Lower Bound",
    conf.high = "Upper Bound"
  )
```

***

* ACOs who started in 2012 report an average of $7,653,639 in savings on average.

* The average savings for ACOs who started each subsequent year decreases by $1,059,183.



Column {.tabset}
-------------------------------------

### Starting Year and Generated Savings / Losses

```{r}


year_results <- aco %>%
  ggplot(aes(x = as.Date(Initial_Start_Year, format = "%Y"), y = GenSaveLoss)) +
  geom_jitter(aes(color = GenSaveLoss_categorical), alpha = 0.6) +
  geom_smooth(method = "lm", se = FALSE, color = "black", size = 0.5) +
  scale_y_continuous(labels = scales::comma) + 
  theme_classic() +
  theme(
    axis.line = element_blank(),
    axis.ticks = element_blank(),
    panel.grid.major.y = element_line(colour = "lightgray", linetype = "dotted"),
    panel.grid.minor.y = element_line(colour = "lightgray", linetype = "dotted"),
    legend.position = "top"
  ) +
  labs(
    x = "Initial Start Year",
    y = "Generated $",
    color = "Category"
  )

year_results

```

### Breakdown of Ages 

```{r}

test <- aco %>%
  select(ACO_ID, GenSaveLoss, GenSaveLoss_categorical, starts_with("perc_Age")) %>%
  pivot_longer(cols = starts_with("perc_Age"),
               names_to = "Age",
               values_to = "Percent",
               names_prefix = "perc_Age_") %>%
  mutate(Age = case_when(Age == "0_64" ~ "0 to 64",
                         Age == "65_74" ~ "64 to 74",
                         Age == "75_84" ~ "75 to 84",
                         Age == "85plus" ~ "85 and up"))
       
test %>%
  group_by(GenSaveLoss_categorical, Age) %>%
  summarize(average = mean(Percent)) %>%
  ggplot(aes(x = GenSaveLoss_categorical, y = average)) +
  geom_col(aes(fill = Age), position = "stack", width = 0.6) +
  coord_flip() +
  theme_minimal() +
  theme(
    axis.title = element_blank(),
    axis.line.x = element_blank()
  )

```


