---
title: "Regression"
output: 
  flexdashboard::flex_dashboard:
    theme: paper
    
runtime: shiny
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)

library(tidyverse)
library(ggplot2)
library(infer)
library(broom)

aco <- readRDS("clean_data/aco.RDS")
county <- readRDS("clean_data/county.RDS")
```

```{r}

acos <- aco %>%
    rep_sample_n(size = nrow(aco),
                 reps = 100,
                 replace = TRUE) %>%
    group_by(replicate) %>%
    nest() %>%
    mutate(mod = map(
      data,
      ~ lm(Sav_rate ~ Initial_Start_Year + ratio_AB_to_providers + current + QualScore,
        data = .
      )
    ),
    reg_results = map(mod, ~ tidy(., conf.int = TRUE))) %>%
    unnest(reg_results) %>%
    select(-data,-mod) %>%
    mutate(
      term = case_when(
        term == "(Intercept)" ~ "Intercept",
        term == "Initial_Start_Year2013" ~ "Initial Starting Year in 2013",
        term == "Initial_Start_Year2014" ~ "Initial Starting Year in 2014",
        term == "Initial_Start_Year2015" ~ "Initial Starting Year in 2015",
        term == "Initial_Start_Year2016" ~ "Initial Starting Year in 2016",
        term == "Initial_Start_Year2017" ~ "Initial Starting Year in 2017",
        term == "Initial_Start_Year2018" ~ "Initial Starting Year in 2018",
        term == "ratio_AB_to_providers" ~ "Ratio of Assigned Beneficiaries to Providers",
        term == "currentTrack 1 Plus" ~ "Track 1 Plus",
        term == "currentTrack 2" ~ "Track 2",
        term == "currentTrack 3" ~ "Track 3",
        term == "QualScore" ~ "Data Quality Score"
      ),
      term = as.factor(term)
    )

provider <- aco %>%
    mutate(N_total_providers = N_total_providers / 100) %>%
    rep_sample_n(size = nrow(aco),
                 reps = 100,
                 replace = TRUE) %>%
    group_by(replicate) %>%
    nest() %>%
    mutate(mod = map(
      data,
      ~ lm(Sav_rate ~ perc_PCP + perc_Spec + N_total_providers,
        data = .
      )
    ),
    reg_results = map(mod, ~ tidy(., conf.int = TRUE))) %>%
    unnest(reg_results) %>%
    select(-data,-mod) %>%
    mutate(
      term = case_when(
        term == "(Intercept)" ~ "Intercept",
        term == "perc_PCP" ~ "% PCP Providers",
        term == "perc_Spec" ~ "% Speciality Providers",
        term == "N_total_providers" ~ "Number of Total Providers"
      ),
      term = as.factor(term)
    )


patient <- aco %>%
    rep_sample_n(size = nrow(aco),
                 reps = 100,
                 replace = TRUE) %>%
    group_by(replicate) %>%
    nest() %>%
    mutate(mod = map(
      data,
      ~ lm(
        Sav_rate ~ perc_Age_65_74 + perc_Age_75_84 + perc_Age_85plus + perc_male,
        data = .
      )
    ),
    reg_results = map(mod, ~ tidy(., conf.int = TRUE))) %>%
    unnest(reg_results) %>%
    select(-data,-mod) %>%
    mutate(
      term = case_when(
        term == "(Intercept)" ~ "Intercept",
        term == "perc_Age_65_74" ~ "% Beneficiaries Age 65-74",
        term == "perc_Age_75_84" ~ "% Beneficiaries Age 75-84",
        term == "perc_Age_85plus" ~ "% Beneficiaries Age 85 +",
        term == "perc_male" ~ "% Beneficiaries Male",
      ),
      term = as.factor(term)
    )
```


Regression {.sidebar}
-------------------------------------

Here we examine the effects of *Patient* factors, *Provider* factors, and *ACO* factors on the **Savings Rate** using a multi-variate linear regression. The results of the 100 simulations of the regression are plotted. Each row represents the estimate produced by a single simulation, with error bars for the estimated value.

**Dropdowns only work on corresponding panels**.



```{r}
selectInput(inputId = "patient_term",
            label = "Patient Factors",
            choices = patient$term,
            selected = unique(patient$term)[1])

selectInput(inputId = "provider_term",
            label = "Provider Factors",
            choices = provider$term,
            selected = unique(provider$term)[1])

selectInput(inputId = "aco_term",
            label = "ACO Factors",
            choices = acos$term,
            selected = "Intercept") 
```



Regression {.tabset}
-------------------------------------

### Patient

```{r}
renderPlot({
  
  mean <- patient %>% filter(term == input$patient_term) %>%
    pull(estimate) %>%
    mean()
  
  patient %>%
    filter(term == input$patient_term) %>%
    ggplot(aes(x = reorder(replicate,-estimate))) +
    geom_point(aes(y = estimate, color = estimate > 0)) +
    geom_errorbar(aes(ymin = conf.low, ymax = conf.high)) +
    geom_hline(yintercept = mean) +
    coord_flip() +
    theme_minimal() +
    theme(
      axis.text.y = element_blank(),
      axis.ticks = element_blank(),
      panel.grid.major.y = element_blank()
    ) +
  labs(
    x = "Savings Rate Estimate",
    y = "Simulations",
    subtitle = "Results of 100 Simulations",
    title = paste("Mean of Estimates of ", input$patient_term, "is ", round(mean, 3))
  )
})
```

 term == "(Intercept)" ~ "Intercept",
        term == "perc_Age_65_74" ~ "% Beneficiaries Age 65-74",
        term == "perc_Age_75_84" ~ "% Beneficiaries Age 75-84",
        term == "perc_Age_85plus" ~ "% Beneficiaries Age 85 +",
        term == "perc_male" ~ "% Beneficiaries Male",
      ),

> **Intercept**: The average savings rate when all other variables are equal to 0. Defaults are: All beneficiaries are 0-64 and female.
  **% Beneficiaries Age 65-74** : The average change in Savings Rate with a 1% increase in the percentage of Beneficiaries between ages 65-74, holding all other variables constant.
  **% Beneficiaries Age 75-84** : The average change in Savings Rate with a 1% increase in the percentage of Beneficiaries between ages 75-84, holding all other variables constant.
  **% Beneficiaries Age 85+** : The average change in Savings Rate with a 1% increase in the percentage of Beneficiaries age 85 and older, holding all other variables constant.
  **% Specialist Providers** : The average change in Savings Rate with a 1% increase in the percentage of Specialist Providers, holding all other variables constant.

### Providers

```{r}
renderPlot({
  
  # patient %>% head()
  
  mean <- provider %>% filter(term == input$provider_term) %>%
    pull(estimate) %>%
    mean()
  
  provider %>%
    filter(term == input$provider_term) %>%
    ggplot(aes(x = reorder(replicate,-estimate))) +
    geom_point(aes(y = estimate, color = estimate > 0)) +
    geom_errorbar(aes(ymin = conf.low, ymax = conf.high)) +
    geom_hline(yintercept = mean) +
    coord_flip() +
    theme_minimal() +
    theme(
      axis.text.y = element_blank(),
      axis.ticks = element_blank(),
      panel.grid.major.y = element_blank()
    ) +
  labs(
    x = "Savings Rate Estimate",
    y = "Simulations",
    subtitle = "Results of 100 Simulations of Linear Regression",
    title = paste("Mean of Estimates of ", input$provider_term, "is ", round(mean, 3))
  )
})
```

> **Intercept**: The average savings rate when all other variables are equal to 0. Defaults are: 0%     PCPs, 0% Specialists, 0 Providers. This value does not have a meaningful interpretation in this   context.
  **% PCP Providers** : The average change in Savings Rate with a 1% increase in the number of PCP Providers, holding all other variables constant.
  **% Specialist Providers**: The average change in Savings Rate with a 1% increase in the number of Specialist Providers, holding all other variables constant.
  **Number of Total Providers**: The average change in Savings Rate when the number of any type of providers increases by 100, holding all other variables constant.



### ACO

```{r}
renderPlot({
  
  # patient %>% head()
  
  mean <- acos %>% filter(term == input$aco_term) %>%
    pull(estimate) %>%
    mean()
  
  acos %>%
    filter(term == input$aco_term) %>%
    ggplot(aes(x = reorder(replicate,-estimate))) +
    geom_point(aes(y = estimate, color = estimate > 0)) +
    geom_errorbar(aes(ymin = conf.low, ymax = conf.high)) +
    geom_hline(yintercept = mean) +
    coord_flip() +
    theme_minimal() +
    theme(
      axis.text.y = element_blank(),
      axis.ticks = element_blank(),
      panel.grid.major.y = element_blank()
    ) +
  labs(
    x = "Savings Rate Estimate",
    y = "Simulations",
    subtitle = "Results of 100 Simulations",
    title = paste("Mean of Estimates of ", input$aco_term, "is ", round(mean, 3))
  )
})
```

> **Intercept**: The average savings rate when all other variables are equal to 0. Defaults are: Age
  **Initial Starting Year** Terms: The average change in Savings Rate if the starting year was selected, holding all other variables constant.
  **Ratio of Assigned Beneficiaries to Providers**: The average change in Savings Rate when the ratio of increased by 1 unit, holding all other variables constant.

