---
title: "Results"
output: 
  flexdashboard::flex_dashboard:
    orientation: columns
    vertical_layout: fill
    storyboard: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)

library(tidyverse)
library(ggplot2)

aco <- readRDS(file = "data/aco.RDS")
county <- readRDS(file = "data/county.RDS")
```

### There are fewer ACOs still participating year over year


```{r}
aco %>% 
  group_by(Initial_Start_Year) %>%
  count %>%
  ggplot(aes(x = Initial_Start_Year, y = n)) +
  geom_col(aes(fill = n)) +
  geom_label(aes(label = n), show.legend = FALSE, vjust = -.2) + 
  scale_y_continuous(limits = c(0, 130)) + 
  theme_classic() +
  theme(
    axis.ticks = element_blank(),
    axis.line = element_blank(),
    axis.text.y = element_blank(),
    axis.title = element_blank(),
    legend.position = "none"
  ) +
  labs(
    title = "The Initial Start Year for ACOs in 2018"
  ) 
```

***

* In 2018, there were a total of `r nrow(aco)` ACOs. While 123 new ACOs joined that year, only a handful of ACOs have persisted since the beginning. 

* These ACOs served `r sum(aco$N_AB)` patients / beneficiaries in a single year. 

* `r sum(aco$N_total_providers)` providers, including primary care physicians (PCPs), specialists, nurse practitioners, physician assistants, clinical nurse specialists participated in the performance year.
  
### Most ACOs choose the risk-less track



```{r}
aco %>% 
  count(current) %>%
  ggplot(aes(current, n)) +
  geom_col()
```


> Track 1 ACOs are one-sided risk. In other words, if the ACO meets the savings threshold, they can share in the rewards.  


### The majority of ACOs did not see any savings or losses



```{r}
aco %>%
  count(GenSaveLoss_categorical) %>%
  ggplot(aes(x = GenSaveLoss_categorical, y = n)) +
  geom_col() +
  geom_text(aes(label = n), show.legend = FALSE, vjust = -1) + 
  scale_y_continuous(limits = c(0, 280)) + 
  theme_classic() +
  theme(
    axis.ticks = element_blank(),
    axis.line = element_blank(),
    axis.text.y = element_blank(),
    axis.title = element_blank(),
    legend.position = "none"
  ) +
  labs(
    title = " "
  ) 

```

> In order to be eligible for savings or penalized for losses, all ACOs have a **Minimum Savings Rate (MSR)** or **Minimum Loss Rate (MLR)**



### Older ACOs are more likely to see savings 


```{r}
aco %>% 
  group_by(Initial_Start_Year, GenSaveLoss_categorical) %>%
  count %>%
  ggplot(aes(x = Initial_Start_Year, y = n)) +
  geom_col(aes(fill = GenSaveLoss_categorical), position = "fill") +
  theme_classic() +
  theme(
    axis.ticks = element_blank(),
    axis.line = element_blank(),
    axis.text.y = element_blank(),
    axis.title = element_blank(),
    legend.position = "bottom"
  ) +
  labs(
    title = "The Initial Start Year for ACOs in 2018",
    fill = "Results"
  ) 
```

```{r}
aco %>% 
  group_by(Initial_Start_Year, GenSaveLoss_categorical) %>%
  count %>%
  ggplot(aes(x = Initial_Start_Year, y = n)) +
  geom_col(aes(fill = GenSaveLoss_categorical), position = "stack") +
  theme_classic() +
  theme(
    axis.ticks = element_blank(),
    axis.line = element_blank(),
    axis.text.y = element_blank(),
    axis.title = element_blank(),
    legend.position = "bottom"
  ) +
  labs(
    title = "The Initial Start Year for ACOs in 2018",
    fill = "Results"
  ) 
```


